---
title: "Alcohol vs Seat choice"
author: "Kaylie Fagoaga"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??
 
 The data came from UCDavis in the year 
 
 $H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.

# Methods

In the data set davisdata Seat is a categorical variable, alcohol is numerical

We try to predict alcohol ~ Seat sp we use the Numerical ~ Categorical helper file

# Results

## Descriptive Results 

### Graphical Summary 

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The boxplot shows the back seat has the highest consume of alcohol than in the front or middle seats 


### Numerical Summary 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows that the backseat consumes about 55% of alcohol, the front consumes about 20% of alcohol and the middle is about 35% of alcohol. This means that the back seats consumes more alcohol than the front or middle seats.  


### Inferential Results 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116, less than 0.05 so we reject the null hypothesis 
There is a difference in alcohol consumption on where people sit


### get fancy 
```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```



```{r}
plot(TukeyHSD(model1))
```


## Conclusions


